Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
Update main.tex

%we'll probably have a group number later
%names are given in alphabetical order
\author{Stuttgart Team: Florian Dreyer (3667877) \and Ekaterina Kolos \and Daria Matiash (3668740)}

@@

\paragraph{Metrics}
We'll evaluate model's performance with question answering accuracy domain-wise in order to have a fair comparison with leaderboards.

>>>>

%we'll probably have a group number later
%names are given in alphabetical order
\author{Stuttgart Team: Florian Dreyer (3667877) \and Ekaterina Kolos (3688474) \and Daria Matiash (3668740)}

@@

\paragraph{Metrics}
We'll evaluate model's performance with question answering accuracy domain-wise in order to have a fair comparison with leaderboards. A few metrics used in machine translation such as BLEU-1, BLEU-4 and BERTScore can also be used, but the main metric we'll rely on is accuracy for question answering.
